Real-space computation of $E$/$B$-mode maps I: Formalism and Compact Kernels

### 2018-06-15 articles/formalism/sections/generalizedeb.tex
added discussion on scaling of the radial kernel and comparison to Zaldariagga. Added reference to real space decomposition of Q/U to its E/B counterparts

%--------------------------------------------------------
\subsubsection{Relation to the spin raising $\eth^2$ and lowering $\bar{\eth}^2$ operators}
Recall that on operating twice with the spin lowering operator on the Stokes charge ${}_{+2}X$ results in filtered version of $E/B$ maps as in \eq{eq:ebdef}. Now note that it is possible to construct a modified real space operator by choosing the harmonic space function to be $g_{\ell} = \sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$, resulting in similarly filtered $E/B$ maps as follows:
%
\beq 
\label{eq:bl_ebdef_lower}
[\mathcal{E} + i \mathcal{B}](\hat{n}_e)=- \Delta \Omega\sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace  \left[  \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}} {}_{+2}X(\hat{n}_{q}) \Bigg\rbrace \,. 
\eeq
%
Comparing \eq{eq:ebdef_lower} to \eq{eq:bl_ebdef_lower} makes apparent the following mapping:
%
\beq
\bar{\eth}^2 \equiv \Delta \Omega \sum_{q=1}^{N_{\rm pix}} \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}}\,.
\eeq
%
The operator $\bar{\eth}^2$ is composed of derivative operations and hence has an implicit bi-positional dependence for all numerical purposes which is made explicit in the band limited version of the operator.  The band limited version of the spin raising operator $\eth^2$ is derived by merely taking the conjugate of the above equation.
%--------------------------------------------------------

>>>>

%--------------------------------------------------------
\subsubsection{Relation to the spin raising $\eth^2$ and lowering $\bar{\eth}^2$ operators}
Recall that on operating twice with the spin lowering operator on the Stokes charge ${}_{+2}X$ results in filtered version of $E/B$ maps as in \eq{eq:ebdef}. Now note that it is possible to construct a modified real space operator by choosing the harmonic space function to be $g_{\ell} = \sqrt{\frac{(\ell+2)!}{(\ell-2)!}}$, resulting in similarly filtered $E/B$ maps as follows:
%
\beq 
[\mathcal{E} + i \mathcal{B}](\hat{n}_e)=- \Delta \Omega\sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace  \left[  \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}} {}_{+2}X(\hat{n}_{q}) \Bigg\rbrace \,.\label{eq:bl_ebdef_lower} 
\eeq
%
Comparing \eq{eq:ebdef_lower} to \eq{eq:bl_ebdef_lower} makes apparent the following mapping:
%
\beq
\bar{\eth}^2 \equiv \Delta \Omega \sum_{q=1}^{N_{\rm pix}} \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}}\,.
\eeq
%
The operator $\bar{\eth}^2$ is composed of derivative operations and hence has an implicit bi-positional dependence for all numerical purposes which is made explicit in the band limited version of the operator.  The band limited version of the spin raising operator $\eth^2$ is derived by merely taking the conjugate of the above equation.
%--------------------------------------------------------

### 2018-06-15 articles/formalism/sections/kernel_discussion.tex
added discussion on scaling of the radial kernel and comparison to Zaldariagga. Added reference to real space decomposition of Q/U to its E/B counterparts

\comment{Compare the fitted slope to the one in the Zaldariaga paper.}

>>>>

\comment{Compare the fitted slope to the one in the Zaldariaga paper.}
\revisit{In the flat sky limit it has been argued that form of the radial function has to be ${}_\mm f(\beta)\simeq\beta^{-2}$ so as to ensures that the Fourier modes for Stokes parameters $Q/U$ are related  to the $E/B$ Fourier modes merely by rotations and with no scale dependent factor \cite{Zaldarriaga2001a}. In this work we formally derive the function form of ${}_\mm f(\beta)$, which is seen to have an oscillatory nature and find that that the envelope of the function scales as $\beta^{-1.55}$.}
\comment{So whats the point and is this discussion better suited for the conclusions? Could the fit by eye be highly misleading? }

### 2018-06-15 articles/formalism/sections/kernel_paintbrush.tex
added discussion on scaling of the radial kernel and comparison to Zaldariagga. Added reference to real space decomposition of Q/U to its E/B counterparts

The intuition from the real-space kernels holds also when we distort the shape of the filament.  If the filament were bent around into a circle, the positive and negative parts of the $B$ pattern will cancel, and we are left with a hoop of pure $E$ pattern (note that this cancellation would not happen for an ellipse or any loop of non-contant radius of curvature).  The same general description holds for a spiral-shaped filament, which can can be viewed as distortion of the straight filament.  The filament is highlighted by positive $E>0$.  The $E$-pattern is more negative on the interior of a curve than on the exterior, and the concentric rings of filamentary structure make an increasingly negative $E$ value inside.  The $B$-pattern is again concentrated at the ends of the filament in an oriented pair of positive/negative fluctuations. \revisit{The spiral filament showcased in \fig{fig:polfilaments} has a constant radius of curvature and thats the reason for not seeing a B-mode signal in intermediate regions of the spiral. For filaments that don't have a constant radius of curvature one expects to generate more B-mode power.} \comment{This is an important point right? So even if the magnetic field is perfectly aligned with the filament, one can generate B-mode signal in intermediate regions of the filament just by having the filament with changing radius of curvature. There is no reason for filaments to have a constant radius of curvature.}

@@

>>>>

The intuition from the real-space kernels holds also when we distort the shape of the filament.  If the filament were bent around into a circle, the positive and negative parts of the $B$ pattern will cancel, and we are left with a hoop of pure $E$ pattern (note that this cancellation would not happen for an ellipse or any loop of non-contant radius of curvature).  The same general description holds for a spiral-shaped filament, which can can be viewed as distortion of the straight filament.  The filament is highlighted by positive $E>0$.  The $E$-pattern is more negative on the interior of a curve than on the exterior, and the concentric rings of filamentary structure make an increasingly negative $E$ value inside.  The $B$-pattern is again concentrated at the ends of the filament in an oriented pair of positive/negative fluctuations. \revisit{The spiral filament showcased in \fig{fig:polfilaments} has a constant radius of curvature and thats the reason for not seeing a B-mode signal in intermediate regions of the spiral. For filaments that don't have a constant radius of curvature one expects to generate more B-mode power.} \comment{This is an important point right? So even if the magnetic field is perfectly aligned with the filament, one can generate B-mode signal in intermediate regions of the filament just by having the filament with changing radius of curvature. There is no reason for filaments to have a constant radius of curvature. Maybe its important to make this demonstration?}

@@

\revisit{Our conclusions differ subtly from those presented in \cite{Zaldarriaga2001a}, where in it is argued that that filaments cannot produce B-mode signals for configurations in which the polarization vector is parallel or perpendicular to the length of the filament. While this conclusion is true for filaments of infinite length, in reality we expect filaments that are observed on the sky to have a finite length and in this case one expects a definite B-mode pattern from the edges of the filament. One also does not expect that filaments have a constant radius of curvature and this will result in an additional generation of B-mode power.} \comment{Move to conclusions?}
